MCC Models

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
correct "it's" -> "its"
update supplement

As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term. It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context. For adults, we used the data from Experiment 1 to infer $\alpha$. That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1. We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.

For children, $\alpha$ changed with age. Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data. As for adults, this was done via the integration model with equal prior probability for each object. In this model, $\alpha$ for a given age was defined via a simple linear regression. Again, we performed a Bayesian analysis to compute a posterior distribution for the intercept and the slope of this regression. In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0).

@@

For children, we used the data from Experiment 6 to model the slope and intercept that best described the developmental trajectory in the data for each of the two conditions. As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age. We used a simple logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6. In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition (same or different speaker), adding the slope times the child's age and then using a logistic transformation to convert the outcome into proportions. Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalized in the same way for adults. The overall distribution then depended on the alignment of information sources in the same way as it did for adults. Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd`.

@@

Here we report details on the model comparisons. Model fit was assessed based on marginal log-likelihoods of the data under each model. Bayes Factors were computed by first subtracting log-likelihoods for two models and then exponentiating the result. Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3. We did not pre-register the inclusion of the noise parameter for Experiment 3, but did so for all subsequent experiments for which we did model comparisons (4 and 7). The first row in Table \ref{tab:ex3_comp} compares the integration model with noise parameter to the model without the noise parameter. This comparison shows that including the noise parameter greatly improves model fit. Figure \ref{fig:modelpredex3} correlates model predictions from the models including noise parameters to the data from Experiment 3.

>>>>

As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term. Its interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context. For adults, we used the data from Experiment 1 to infer $\alpha$. That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1. We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.

For children, $\alpha$ changed with age. Thus, $\alpha$ for a given age was defined via a simple linear regression and instead of inferring a single value across age, we used the data from Experiment 5 to find the intercept ($\beta^\alpha_0$) and slope ($\beta^\alpha_1$) that best described the developmental trajectory in the data. As for adults, this was done via the integration model with equal prior probability for each object. We performed a Bayesian analysis to compute a posterior distribution for the intercept and the slope of this regression. The prior distribution was $\beta^\alpha_0 \sim {\rm Cauchy }(1,2)$ for the intercept and $\beta^\alpha_1 \sim {\rm Cauchy }(0,2)$ for the slope. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in. In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0): $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$.

@@

For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the $j$ two conditions. As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age. We used a simple Bayesian logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6. The prior distribution was $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ for the intercept and slope. We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in. In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition ($j$), adding the slope times the child's age ($i$) and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$. Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalization in the same way as for adults. The overall distribution then depended on the alignment of information sources in the same way as it did for adults. Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd` starting line 1491.

@@

Here we report details on the model comparisons. Model fit was assessed based on marginal log-likelihoods of the data under each model. To compute the log-likelihood for models including a noise parameter, we used forward sampling on four independent chains to collect 5000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.

Bayes Factors were then computed by first subtracting log-likelihoods for two models and then exponentiating the result. Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3. We did not pre-register the inclusion of the noise parameter for Experiment 3, but did so for all subsequent experiments for which we did model comparisons (4 and 7). The first row in Table \ref{tab:ex3_comp} compares the integration model with noise parameter to the model without the noise parameter. This comparison shows that including the noise parameter greatly improves model fit. Figure \ref{fig:modelpredex3} correlates model predictions from the models including noise parameters to the data from Experiment 3.

### 2020-09-22 papers/full_paper/manuscript.Rmd
update supplement

We preregistered sample sizes, inferential statistical analysis and computational models for all experiments. All deviations from the registered analysis plan are explicitly mentioned. All analyses were run in R [@R-base]. All p-values are based on two sided analysis. Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests. Frequentist logistic GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence. Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material available online.

Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian]. All models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl]. In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data. Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online. Code to run the models is available in the associated online repository.

>>>>

We preregistered sample sizes, inferential statistical analysis and computational models for all experiments. All deviations from the registered analysis plan are explicitly mentioned. All analyses were run in R [@R-base]. All p-values are based on two sided analysis. Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests. Frequentist logistic GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence. Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material.

All models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl]. Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in WebPPL. In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data. Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online. Code to run the models is available in the associated online repository.
